\documentclass{article}
\usepackage{hyperref}

\title{DANNY TABAREZ}
\author{}
\date{}

\begin{document}

\maketitle

\section*{Contact Information}

\begin{itemize}
  \item \textbf{Email:} dan.tabarez@gmail.com
  \item \textbf{Phone number:} +593 987027519
  \item \textbf{Website:} \url{https://www.linkedin.com/in/danny-tabarez/}
  \item \textbf{GitHub:} \url{https://github.com/dantabarez}
\end{itemize}

\section*{Skills}

\begin{itemize}
  \item Problem-Solving and Administration skills, Automation and Scripting, Security and Monitoring.
  \item Special experience on C2IS and Mobile systems.
\end{itemize}

\section*{Areas of Knowledge}

\begin{itemize}
  \item Managing RHEL servers in Production.
  \item Avid Linux user.
  \item Working with VMware, Netapp, HP, Cisco technologies.
  \item Experience leading a team of +5 people.
  \item Good knowledge of new technologies in general.
  \item Learning on my own: Python, Git, Docker, AWS.
\end{itemize}

\section*{Professional Experience}

\subsection*{Indra - Lead Sysadmin (July 2018 – Present)}

\begin{itemize}
  \item Managing more than 3 production datacenters of C2IS infrastructure and more than 48 RHEL and Debian servers.
  \item Technical leader for over 100+ end users.
  \item VCenter management, Netapp storage provisioning.
  \item Helped design the process of long-term data archiving using a tape cabin.
  \item Worked on automation of processes, log backup, scripting for bugs and problems.
  \item Remote assistance for problem solving, patching and installation of new features.
\end{itemize}

\subsection*{Cellopti – Telecom engineer (April 2015 – June 2018)}

\begin{itemize}
  \item IT manager and mobile tester (SSV-SFT-DT) for LTE sites around 10 cities of Ecuador.
  \item Helped mount small business IT infrastructure from zero; networking services, storage, firewall configuration for VPN and cVPN, public FTP server for mobile speed tests.
  \item Template and automation of Tems Discovery reports.
\end{itemize}

\subsection*{Sonda – N1 technical support (March 2014 – August 2014)}

\begin{itemize}
  \item Monitoring and technical support at Movistar ISP service, 24/7 requirements.
\end{itemize}

\subsection*{Volunteer: Campus Party 2011 as CRM \& 2014 as Technical Support and Installation}

\section*{Languages}

\begin{itemize}
  \item English (Basic), Portuguese (Basic), Spanish (native).
\end{itemize}

\section*{Hobbies}

\begin{itemize}
  \item Car customization and off-road driving.
  \item Listening to music.
  \item Building custom PCs.
\end{itemize}

\end{document}
